LAGOS lake depth

### 2021-08-04 figures/02_depth_model.Rmd
turn off 02_depth_model_fitted chunk for now

```{r 02_depth_model_fitted, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
dt <- readRDS("../data/01_depth_model/depth_model.rds")

>>>>

```{r 02_depth_model_fitted, echo=FALSE, message=FALSE, eval=FALSE, warning=FALSE, results='hide'}
dt <- readRDS("../data/01_depth_model/depth_model.rds")
